DeepPicar: A Low-cost Deep Neural Network-based Autonomous Car

### 2018-01-30 paper/related.tex
Add initial paragraphs in related works
Added initial sections on the Google Object Detection API and Donkey Car
to the related works section.

@@

>>>>

While we were able to show that a smaller embedded platform like the 
Raspberry Pi 3 can successfully run a DNN, it should be noted that the
network architecture, and hence model, used was relatively small. Other 
available DNN's can be much larger compared to the architecture of the
DAVE-2. Such DNN's can be seen in Google's Object Detection API~\cite{huang2017speed}.
The smallest model available in the API is the MobileNet model, which
has 3,191,072 parameters and is approximately 12.7 larger than the
model used by the DeepPicar. The other models all have parameter sizes 
of at least 10 million. Due to the considerable differences in the 
model sizes, it is likely that running them on platforms like the Pi 3,
and still get acceptable real-time performance would be difficult, 
if not infeasible.

@@

Another autonomous vehicle platform is the Donkey Car\footnote{https://donkeycar.com}.
Like the DeepPicar, the Donkey Car is a low cost platform that can be 
utilized for researching self-driving cars. However, comparatively, the
DeepPicar is approximately \$200 cheaper than the Donkey Car. 
Furthermore, the Donkey Car was created with an emphasis on model accuracy
and the ability of the car to navigate the desired environment. We are 
more focused on the real-time performance of the DeepPicar, and whether
the Raspberry Pi 3 embedded computing platform can properly support autonomous 
vehicle operations. To the best of our knowledge, no other studies have
been done to evaluate the capabilities of the Pi 3 for running DNNs and
performing autonomous vehicle operations.
